\bf Faster Neural Machine Translation Inference

### 2018-02-08 fast-beam/fast-beam.tex
fast beam paper

In fact, we are usually only interested in the best class during inference, not the probability. Since we now calculate the best class before the softmax, we can skip softmax altogether, Algorithm~\ref{algo:Argmax only}. However, is this only possible for beam size 1; the comparison between softmax probobilities is required for larger beam sizes as the denominator is different in different beams.

>>>>

In fact, we are usually only interested in the best class during inference, not the probability. Since we now calculate the best class before the softmax, we can skip softmax altogether, Algorithm~\ref{algo:Argmax only}. However, this is only possible for beam size 1; the comparison between softmax probobilities is required for larger beam sizes as the denominator is different in different beams.
